Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 testbed.tex
worked on testbred

\subsection{Download image}

>>>>

The first thing we need to do is to download the linux installation file.
For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.

Raspbian is made available in two bundles. Raspbian and Raspbian lite.
The difference between the two is that Raspbian contains a pre-installed desktop
environment, and Raspbian lite is by default only accessable through a shell. 
They will both also be remotely accessible using \ac{SSH}.

Our testbed does not have monitors so we will install Raspbian lite.
A desktop environment can always be installed manually in case that will be
desired sometime in the future.

Below is a procedure of how we setup the \ac{Raspi}s in our testbed. We
have decided a simple setup where each \ac{Raspi} is equipped with a
memory card that contains a slightly customized Raspbian lite image with
identical settings.

The reason this can be done easily is because the official Raspbian lite image
that we will download simply conntains a complete linux installation that are
packaged in an image rather than written to a harddrive, memory card, or usb
pen.

The overall steps to customize the official Raspbian lite image are listed below:
\begin{enumerate}
    \item Download Raspbian lite
    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
        in the official Raspbian lite image
    \item Change root. I.e. change root filesystem into the Raspbian lite
        image to update and install software packages
    \item Write image to memory cards
\end{enumerate}

\subsection{Download Raspbian lite}
